### 2012-02-22 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\STATE $stepNodes =$ an empty array
\STATE $forBoundSubsteps =$ an empty associative array
\FORALL{$stepNode \in pathExprNode.getChildren()$}
	\STATE $detailNode = stepNode.getChild(DetailNode)$
	\IF{$detailNode != null$}
		\IF{$is(detailNode, VarRefNode)$}
			\STATE $type = getType(detailNode)$ // $PathType$
			\IF{$type.isForBound$}
				\STATE $forBoundSubsteps[stepNode] = type$
				\STATE add $stepNode$ to $stepNodes$
			\ELSE
				\STATE add all $type.stepNodes$ to $stepNodes$
			\ENDIF
		\ELSE
			\STATE add $stepNode$ to $stepNodes$
		\ENDIF
	\ELSE
		\STATE add $stepNode$ to $stepNodes$
	\ENDIF
\ENDFOR

@@

\FORALL{$bindingNode \in bindingNodes$}
    \STATE $bindingExpr = bindingNode.getChild(BindingSequenceNode).$ $getChild(ExprNode)$
    \IF{$getType(BindingExpr) == PathType$ using only child and descendant axes, ending with exactly one predicate $P$}
        \FORALL{$(var, node) \in forVars$}
            \STATE $forVars = determinateJoinPatterns(bindingNode, P, node, var,$ $forVars)$
        \ENDFOR
    \ELSIF{$getType(BindingExpr) == PathType$ without predicates using only child and descendant axes}
        \IF{$is(bindingNode, ForClauseNode$}
            \STATE add $(bindingNode.varName, bindingNode)$ to forVars
        \ENDIF
    \ENDIF
\ENDFOR

@@

\begin{algorithm}
\caption{Function determinateJoinPatterns}
\label{ALG_func_determinateJoinPatterns}
\begin{algorithmic}[1]
\REQUIRE{\ \\
    $curBindingNode$: A variable binding node in the current FLWOR node. \\
    $P$: A predicate from the binding expression. \\
    $forBindingNode$: A for binding node from an ancestor FLWOR node. \\
    $forVar$: A variable from the ancestor for binding node. \\
    $forVars$: An array of couples of for variables and their for clause nodes.
}

@@

\IF{$is(exprNode, OperatorNode$)}
    \IF{$exprNode.operator == GEN\_EQUALS$}
        \FORALL{$var \in forVars$}
            \IF{$exprNode$ is of a form $var/L = C$ where $L$ is a path without predicates, except the last step, using only child and descendant axes, and C is a literal constant}
                \STATE memorize $var/L$ as the negative key statement, weight 0.9
            \ENDIF
        \ENDFOR
    \ELSIF{$exprNode.operator == AND$}
        \STATE processWhere(forVars, exprNode.leftSide)
        \STATE processWhere(forVars, exprNode.rightSide)
    \ENDIF
\ENDIF

\end{algorithmic}
\end{algorithm}

>>>>

\STATE $stepNodes =$ an empty array
\STATE $forBoundSubsteps =$ an empty associative array
\FORALL{$stepNode \in pathExprNode.getChildren()$}
	\STATE $detailNode = stepNode.getChild(ExprNode)$
	\IF{$detailNode != null$}
		\IF{$is(detailNode, VarRefNode)$}
			\STATE $type = getType(detailNode)$ // $PathType$
			\IF{$type.isForBound$}
				\STATE $forBoundSubsteps[stepNode] = type$
				\STATE add $stepNode$ to $stepNodes$
			\ELSE
				\STATE add all $type.stepNodes$ to $stepNodes$
			\ENDIF
		\ELSE
			\STATE add $stepNode$ to $stepNodes$
		\ENDIF
	\ELSE
		\STATE add $stepNode$ to $stepNodes$
	\ENDIF
\ENDFOR

@@

\FORALL{$bindingNode \in bindingNodes$}
    \STATE $bindingExpr = bindingNode.getChild(BindingSequenceNode).$ $getChild(ExprNode)$
    \IF{$getType(BindingExpr) == PathType$ using only child and descendant axes, ending with exactly one predicate $P$}
        \FORALL{$(var, node) \in forVars$}
            \STATE $forVars = determinateJoinPatterns(bindingNode, P, node, var,$ $forVars,$ $checkJoinPattern3,$ $whereExpr)$
        \ENDFOR
    \ELSIF{$getType(BindingExpr) == PathType$ without predicates using only child and descendant axes}
        \IF{$is(bindingNode, ForClauseNode$}
            \STATE add $(bindingNode.varName, bindingNode)$ to forVars
        \ENDIF
    \ENDIF
\ENDFOR

@@

\begin{algorithm}
\caption{Function determinateJoinPatterns}
\label{ALG_func_determinateJoinPatterns}
\begin{algorithmic}[1]
\REQUIRE{\ \\
    $curBindingNode$: A variable binding node in the current FLWOR node. \\
    $P$: A predicate from the binding expression. \\
    $forBindingNode$: A for binding node from an ancestor FLWOR node. \\
    $forVar$: A variable from the ancestor for binding node. \\
    $forVars$: An array of couples of for variables and their for clause nodes. \\
    $checkJoinPattern3$: A flag determining whether to analyze the join pattern as possible join pattern 3. \\
    $whereExpr$: An expression from a where clause of the current FLWOR node.
}

@@

\IF{$is(exprNode, OperatorNode$)}
    \IF{$exprNode.operator == GEN\_EQUALS$}
        \FORALL{$var \in forVars$}
            \IF{$exprNode$ is of a form $var/L = C$ where $L$ is a path without predicates, except the last step, using only child and descendant axes, and C is a literal constant}
                \STATE memorize $var/L$ as the negative key statement, weight 0.9
            \ENDIF
        \ENDFOR
    \ELSIF{$exprNode.operator == AND$}
        \STATE $processWhere(forVars, exprNode.leftSide)$
        \STATE $processWhere(forVars, exprNode.rightSide)$
    \ENDIF
\ENDIF
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Function usesOnlyChildAndDescendantAxes}
\label{ALG_function_uses_only_child_and_descendant_axes}
\begin{algorithmic}[1]
\REQUIRE $pathType$: A $PathType$ instance.
\ENSURE A boolean result.

\todo[inline]{Dalsie pomocne funkcie a zaradit ich do nejakej kapitoly o pom. funkciach.}
\FORALL{$stepNode \in pathType.stepNodes$}
	\IF{$stepNode.isAxisStep()$}
		\STATE $axisKind = stepNode.getAxisNode().getAxisKind()$
		\IF{$axisKind$ $!=$ $CHILD$ $AND$ $axisKind$ $!=$ $DESCENDANT$}
			\RETURN false
		\ENDIF
	\ENDIF
\ENDFOR

\STATE $detailNode = stepNode.getChild(ExprNode)$
\IF{$detailNode != null$}
	\IF{$is(detailNode, VarRefNode)$}
		\IF{$usesOnlyChildAndDescendantAxes($ $pathType.forBoundSubsteps[stepNode]) ==$ false}
			\RETURN false
		\ENDIF
	\ENDIF
\ENDIF

\RETURN true
\end{algorithmic}
\end{algorithm}
